# Data structures

## SummarizedExperiment

The central data structure for working with high-throughput experimental assay
data in Bioconductor is the `r Biocpkg("SummarizedExperiment")` container.

```{r help, eval=FALSE}
?SummarizedExperiment
```

## ExpressionSet

Previous versions of the `r Biocpkg("EnrichmentBrowser")` used the
`ExpressionSet` data structure.
The migration to `SummarizedExperiment` in the current release of the
`EnrichmentBrowser` is done to reflect recent developments in 
Bioconductor, which discourage use of `ExpressionSet` in favor of 
`SummarizedExperiment`.
Major reasons are the compatibility of `SummarizedExperiment` with 
operations on genomic regions as well as efficient dealing with big data.

To enable a smooth transition, all functions of the `r Biocpkg("EnrichmentBrowser")`
are still accepting also an `ExpressionSet` as input, but are  
consistently returning a `SummarizedExperiment` as output.

Furthermore, users can always coerce from `SummarizedExperiment` to 
`ExpressionSet` via

```{r sexp2eset, eval = FALSE}
eset <- as(se, "ExpressionSet")
```

and vice versa

```{r eset2sexp, eval = FALSE}
se <- as(eset, "SummarizedExperiment")
```

